%----------------------------------------------------------------------------------------
%   Дипломын номзүй, хавсралтын хэсэг эндээс эхэлнэ
%----------------------------------------------------------------------------------------

%----------------------------------------------------------------------------------------
%   ДИПЛОМЫН НОМ ЗҮЙ, ХАВСРАЛТЫН ХЭСЭГ ЭНДЭЭС ЭХЭЛНЭ
%----------------------------------------------------------------------------------------

\singlespace
\addcontentsline{toc}{part}{НОМ ЗҮЙ}
\begin{thebibliography}{99}
    % Ашигласан материалыг эндээс оруулна
    \bibitem{declarative}
    Нарангэрэл, Н., Болд, Л., Өнөрбаян, Ц. ба бусад.
    \textit{Монгол хэлний зөв бичих дурмийн журамласан толь}.
    Улаанбаатар хот, 2022.
    URL: \url{https://toli.gov.mn/}

		\bibitem{ict-terms}
    Чулуунбанди, Н., Лхагвасурэн, Т., Дугарчулуун, Г. ба бусад.
    \textit{Мэдээлэл, харилцаа холбооны технологийн англи нэр томоёоны тайлбар}.
    Линограф, 2018.

    \bibitem{Alistair2005}
    A. Cockburn.
    \textit{Hexagonal Architecture}.
    2005.
    URL: \url{https://alistair.cockburn.us/hexagonal-architecture/}

    \bibitem{ameer2024}
    A. Ameer, F. Khan, and M. Ali.
    \textit{Performance Comparison Between Single Page Application and Micro-frontend Architectures}.
    IEEE Access, vol. 12, pp. 12045–12059, 2024. (ISSN: 2169-3536)

    \bibitem{atlassian_microservices}
    Atlassian.
    \textit{Microservices architecture}.
    URL: \url{https://www.atlassian.com/microservices/microservices-architecture}

    \bibitem{banks2020}
    A. Banks and E. Porcello.
    \textit{Learning React: Modern Patterns for Developing React Apps}.
    2nd ed. O'Reilly Media, 2020.

		\bibitem{beyer2016site}
    B. Beyer, C. Jones, J. Petoff, and N. R. Murphy.
    \textit{Site Reliability Engineering: How Google Runs Production Systems}.
    O'Reilly Media, 2016.

    \bibitem{bjelotomic2024}
    N. Bjelotomic, K. Vucic, and S. Radenkovic.
    \textit{Development Tools for Micro-Frontends: A Comparative Study}.
    International Conference on Web Engineering (ICWE), 2024.

    \bibitem{blinowski2022}
    G. Blinowski, A. Ojdowska, and A. Przybylek.
    \textit{Monolithic vs. microservice architecture: A performance and scalability evaluation}.
    IEEE Access, vol. 10, pp. 20357–20374, 2022.

		\bibitem{chiksen2000flow}
    M. Csikszentmihalyi.
    \textit{Flow: The Psychology of Optimal Experience}.
    HarperCollins Perennial, 2000.

    \bibitem{cypress_docs}
    Cypress.io.
    \textit{Cypress Documentation}.
    URL: \url{https://docs.cypress.io/}

    \bibitem{docker}
    \textit{Docker}.
    URL: \url{https://docs.docker.com/}

    \bibitem{dragoni2017}
    N. Dragoni, S. Giallorenzo, A. L. Lafuente, M. Mazzara, F. Montesi, R. Mustafin, and L. Safina.
    \textit{Microservices: Yesterday, Today, and Tomorrow}.
    Cham: Springer International Publishing, 2017, pp. 195–216.
    URL: \url{https://doi.org/10.1007/978-3-319-67425-4_12}

    \bibitem{esposito2019}
    D. Esposito.
    \textit{Modern Web Development with ASP.NET Core 3}.
    Packt Publishing, 2019.

		\bibitem{evans2003}
    E. Evans.
    \textit{Domain-Driven Design: Tackling Complexity in the Heart of Software}.
    Addison-Wesley Professional, 2003.

    \bibitem{dora}
    N. Forsgren, J. Humble, and G. Kim.
    \textit{Accelerate: The Science of Lean Software and DevOps: Building and Scaling High Performing Technology Organizations}.
    IT Revolution Press, 2018.
		
    \bibitem{fowler_microfrontends}
    \textit{Micro frontends}.
    URL: \url{https://martinfowler.com/articles/micro-frontends.html}

    \bibitem{fowler_strangler}
    M. Fowler.
    \textit{Strangler Fig Application}.
    martinfowler.com, Jun 2004.
    URL: \url{https://martinfowler.com/bliki/StranglerFigApplication.html}

		\bibitem{garcia1987saga}
    H. Garcia-Molina and K. Salem.
    Sagas. 
    \textit{ACM SIGMOD Record}, 16(3), pp. 249-259, 1987.
		
    \bibitem{geers2017}
    M. Geers.
    \textit{Micro frontends}.
    Aug 2017.
    URL: \url{https://micro-frontends.org/}

    \bibitem{geers2020}
    M. Geers.
    \textit{Micro frontends in action}.
    Manning Publications Co., 2020.

    \bibitem{grigorik2013}
    I. Grigorik.
    \textit{High Performance Browser Networking: What Every Web Developer Should Know about Networking and Web Performance}.
    O'Reilly Media, 2013.
    URL: \url{https://hpbn.co/}

    \bibitem{harris_microservices}
    C. Harris.
    \textit{Microservices vs. monolithic architecture}.
    URL: \url{https://www.atlassian.com/microservices/microservices-architecture/microservices-vs-monolith}

    \bibitem{iso25010_1}
    International Organization for Standardization.
    \textit{ISO/IEC 25010:2011 Systems and software Quality Requirements and Evaluation (SQuaRE)}.
    Mar 2019.
    URL: \url{https://www.iso.org/standard/35733.html}

    \bibitem{iso25010_2}
    International Organization for Standardization.
    \textit{ISO/IEC 25010:2011 Systems and software Quality Requirements and Evaluation (SQuaRE)}.
    URL: \url{https://iso25000.com/index.php/en/iso-25000-standards/iso-25010}

    \bibitem{jackson2019}
    C. Jackson.
    \textit{Micro Frontends}.
    martinfowler.com, Nov 2019.
    URL: \url{https://martinfowler.com/articles/micro-frontends.html}

    \bibitem{jest_docs}
    Meta.
    \textit{Jest: Delightful JavaScript Testing}.
    URL: \url{https://jestjs.io/}

    \bibitem{kaushik2015}
    S. Kaushik and R. Somvir.
    \textit{DEMATEL: a methodology for research in library and information science}.
    International Journal of Librarianship and Administration, vol. 6, no. 2, pp. 179–185, 2015.

		\bibitem{Kazman2000}
    R. Kazman, M. Klein, and P. Clements.
    \textit{ATAM: Method for Architecture Trade-off Analysis}.
    Technical Report, Software Engineering Institute, Carnegie Mellon University, 2000.
		
		\bibitem{kegel1999c10k}
    D. Kegel.
    \textit{The C10k Problem}.
    Available at: http://www.kegel.com/c10k.html, 1999.

    \bibitem{kolade2023}
    C. Kolade.
    \textit{Solid design principles in software development}.
    Feb 2023.
    URL: \url{https://www.freecodecamp.org/news/solid-design-principles-in-software-development/}

    \bibitem{kubernetes}
    \textit{Kubernetes}.
    URL: \url{https://kubernetes.io/}

    \bibitem{lighthouse_google}
    Google.
    \textit{Lighthouse}.
    URL: \url{https://developer.chrome.com/docs/lighthouse/}

    \bibitem{madge_docs}
    P. Sundqvist.
    \textit{madge: Create graphs from your CommonJS, AMD or ES6 module dependencies}.
    URL: \url{https://github.com/pahen/madge}

    \bibitem{mannisto2023}
    T. Männistö, J. Tuovinen, and M. Raatikainen.
    \textit{Experiences of transforming a monolithic UI into a micro-frontend solution}.
    Empirical Software Engineering, 2023.

    \bibitem{mdn_import}
    \textit{Developer mozilla}.
    URL: \url{https://developer.mozilla.org/en-US/docs/Web/JavaScript/Reference/Operators/import}

    \bibitem{mezzalira2021}
    L. Mezzalira.
    \textit{Building Micro-Frontends: Scaling Teams and Projects, Empowering Developers}.
    O'Reilly Media, 2021.

    \bibitem{microfrontends_info}
    \textit{Micro-frontends}.
    URL: \url{https://microfrontends.info/microfrontends/}

    \bibitem{mikowski2013}
    M. Mikowski and J. Powell.
    \textit{Single Page Web Applications: JavaScript end-to-end}.
    Manning, 2013.
    URL: \url{https://books.google.se/books?id=eDszEAAAQBAJ}

    \bibitem{mohammed2022}
    S. Mohammed, J. Fiaidhi, D. Sawyer, and M. Lamouchie.
    \textit{Developing a GraphQL SOAP conversational micro frontends for the problem oriented medical record (QL4POMR)}.
    2022 6th International Conference on Medical and Health Informatics, 2022.

    \bibitem{montelius2021}
    A. Montelius.
    \textit{An exploratory study of micro frontends}.
    2021.
    URL: \url{http://urn.kb.se/resolve?urn=urn:nbn:se:liu:diva-176963}

    \bibitem{newman2019}
    S. Newman.
    \textit{Monolith to Microservices: Evolutionary Patterns to Transform Your Monolith}.
    O'Reilly Media, 2019.

    \bibitem{pavlenko2020}
    A. Pavlenko, N. Askarbekuly, S. Megha, and M. Mazzara.
    \textit{Micro-frontends: Application of microservices to web front-ends}.
    Journal of Internet Services and Information Security, vol. 10, no. 2, pp. 49–66, 2020.

    \bibitem{ponce2019}
    F. Ponce, G. Márquez, and H. Astudillo.
    \textit{Migrating from monolithic architecture to microservices: A rapid review}.
    In 2019 38th International Conference of the Chilean Computer Science Society (SCCC), 2019, pp. 1–7.

    \bibitem{silva2024}
    E. T. Silva, R. Pereira, and A. Maciel.
    \textit{Micro-frontends Architecture: A Systematic Literature Review}.
    Journal of Systems and Software, vol. 208, 111874, 2024.

    \bibitem{sonarqube_docs}
    SonarSource.
    \textit{SonarQube Documentation}.
    URL: \url{https://docs.sonarsource.com/sonarqube/}

    \bibitem{stefanovska2022}
    E. Stefanovska and V. Trajkovik.
    \textit{Evaluating micro frontend approaches for code reusability}.
    Communications in Computer and Information Science, p. 93–106, 2022.

    \bibitem{taibi2022}
    D. Taibi and L. Mezzalira.
    \textit{Micro-Frontends: A Software Architecture Perspective}.
    IEEE Software, vol. 39, no. 5, 2022.

		\bibitem{winters2020software}
    T. Winters, T. Manshreck, and H. Wright.
    \textit{Software Engineering at Google: Lessons Learned from Programming over Time}.
    O'Reilly Media, 2020.

    \bibitem{tilak2020}
    P. Y. Tilak, V. Yadav, S. D. Dharmendra, and N. Bolloju.
    \textit{A platform for enhancing application developer productivity using microservices and micro-frontends}.
    In 2020 IEEEHYDCON, 2020, pp. 1–4.

    \bibitem{vuejs}
    \textit{Vuejs}.
    URL: \url{https://vuejs.org/}

    \bibitem{w3schools}
    \textit{W3schools}.
    URL: \url{https://www.w3schools.com/js/js_versions.asp}

    \bibitem{webpack}
    \textit{Webpack}.
    URL: \url{https://webpack.js.org}

    \bibitem{webpack_loaders}
    \textit{Webpack, loaders}.
    URL: \url{https://webpack.js.org/concepts/\#loaders}

    \bibitem{webpack_mf}
    Webpack.
    \textit{Module Federation}.
    URL: \url{https://webpack.js.org/concepts/module-federation/}

    \bibitem{webpack_module}
    \textit{Webpack, module}.
    URL: \url{https://webpack.js.org/configuration/module/}

\end{thebibliography}
